Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-09-27 limits/ms.tex
New plots and updated text.

\documentclass[galley,usenatbib]{mn2e}
%\documentclass[twocolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
\usepackage{myaasmacros}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\Glass\ is an evolution of the concepts employed by the free form modelling tool
\PixeLens\ but completely rewritten in Python and C. The key improvements are:
%
\begin{enumerate}
  \setcounter{enumi}{0}
  \item A modular framework allows new priors to be added and modified easily.
\end{enumerate}
%
Each prior is a simple function that adds linear constraints that operate on either
a single lens object or the entire ensemble of objects. \Glass\ comes with a number
of useful priors, but a user can write their own in the input file.
%
\begin{enumerate}
  \setcounter{enumi}{1}
  \item The basis functions approximating a model can be changed. 
\end{enumerate}
%
\Glass\ currently describes the lens mass as a collection of pixels, but the code
has been designed to support alternative methods. In particular, it is planned
to develop a module using Bessel functions. This will require a new set of 
priors that operate on these functions.
%
\begin{enumerate}
  \setcounter{enumi}{2}
  \item Non-linear constraints can be imposed in an automated post-processing step. 
\end{enumerate}
%
Once \Glass\ has generated an ensemble of models given the linear constraints, any number
of post processing functions can be applied. Not only can these functions be used to
derive new quantities from the mass models, they can also be used as a filter to 
accept or reject a model based on some non-linear constraint. The plotting functions
within \Glass\ will correctly display models that have been accepted or rejected.
%
\begin{enumerate}
  \setcounter{enumi}{3}
  \item The central region can be have a higher resolution to capture steep models. 
\end{enumerate}
%
By default, the mass distribution of the lens is described by uniform grid. However,
in the central region of a lensing galaxy where the mass profile may rise steeply,
a higher resolution can be specified that only applies to the inner pixels. These
pixels are subdivided into a smaller grid. {\bf JR. I think Jonathan is now applying this by default. Is that right Jonathan?} 
%
\begin{enumerate}
  \setcounter{enumi}{4}
  \item Stellar density can be used as an additional constraint.  
\end{enumerate}
%
The mass in inner regions of galaxies is often dominated by the stellar component
which one can estimate using standard mass-to-light models. This data can be added
to the potential as described later in \secref{stellar mass}. By using the stellar
mass one can place a lower bound on the mass and help constrain the inner most
mass profile.
%
\begin{enumerate}
  \setcounter{enumi}{5}
  \item Point or extended mass objects can be placed in the field.
\end{enumerate}
%
\PixeLens\ only allows for a shear term to be added to the potential (as shown
later in \eqnref{shear}) to account for mass external to model region. This
is useful to capture the gross effects of a distant neighbour. \Glass\ also
has a shear term but additional allows for additional analytic potentials to
be included. This can be used to model substructure or multiple neighbors close
to the main lens. The substructure may have only a small effect if the lens is
a single galaxy, but if the lens is group then a potential can be added for
each of the galaxies.
%
\begin{enumerate}
  \setcounter{enumi}{5}
  \item A new uniform sampling algorithm for high dimensional spaces.
\end{enumerate}
%
At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
linear space that represents the modelling solution space. This algorithm was
described and tested in \cite{2012MNRAS.425.3077L}. \Glass\ is also multi-threaded allowing it to
run efficiently on many-cored machines.  The software is freely available for
download. One interesting aspect is that the input files are themselves Python
programs. This allows a large amount of sophistication in setting up a lens at
runtime and also allows \Glass\ to be used as an external library from another
user written program.

@@

@@

Unfortunately, the lens equation and the arrival times alone are not enough to form a
closed volume in the solution space. We have not imposed any strong constraints
on the density even so much as to ensure that it is non-negative everywhere. We
must therefore provide additional linear constraints so that we only sample
physical models. The explicit implementation for these priors has been
explained in \cite{}, but can be summarized as
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope everywhere $\le 0$. This prevents hollow rings.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity is enforced.
\item The density is radially symmetric. (Optional)
\end{enumerate}

@@

\subsection{Removing models with extra images}\label{sec:glassextraimages} 
While linear constraints can be applied on-the-fly in \Glass, non-linear constraints must be applied in post-processing. Models that are inconsistent with such constraints must then be statistically discarded via a likelihood analysis. An example of such a non-linear constraint is the spurious presence of unobserved images. This `null-space' prior was first proposed and explored by \citet{2006MNRAS.367.1209L} and found to be extremely powerful. We find that our gradient prior in \Glass\ (see \S\ref{sec:discrete}), performs much of the same function as \citeauthor{2006MNRAS.367.1209L}'s null-space prior, but some models can still rarely turn up spurious images. We reject these in a post-processing step, where we sweep through the model ensemble applying the ray tracing algorithm described in \ref{Raytracing}. Models are accepted or rejected according to the criteria:

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{MockGalProfile-a.pdf} 
\includegraphics[width=0.33\textwidth]{MockGalProfile-b.pdf} 
\includegraphics[width=0.33\textwidth]{MockGalProfile-c.pdf}
\caption{{\bf JR. Cut the analytic profiles from this Figure. All fonts and labels should be larger. Left panel should start at 0.7kpc.}
\textbf{Left:} 
Density averaged in spherical shells of the four galaxy mocks: AA, AC, BB and BC, showing the stellar (dotted), dark matter (dashed),
and total (solid) densities, respectively. Notice that the stars in models BB and BC contribute significantly to the central potential. 
\textbf{Middle:} 
The radially averaged two-dimensional projected density.
The critical density for lensing at $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$, is marked by the horizontal line. 
\textbf{Right:}
The enclosed projected mass.
}
\label{mock galaxies}
\end{figure*}

@@

For each of the four galaxies, we used the raytracing feature of \Glass\
described in \secref{Raytracing} to construct 12 lensing scenarios {\bf JR. We have 12 lensing scenarios, but only 6 panels in Figure 2. Is this number correct?}:

\begin{enumerate}
\item one double and one extended double;
\item one quad and one extended quad;
\item two 2-source quads with varying redshift contrast.
\end{enumerate}
The `extended' configurations use multiple point sources at the same redshift to simulate an extended source (that will produce an arc-like image). \figref{arrival surfaces} shows the configuration for the extended quad, along with the other cases.

@@

Each of these configurations were modelled with and without time delays and with
and without a central image. (The central image is typically highly demagnified. For galaxy lenses it is very difficult to find since it lies along the sight line to the bright lensing galaxy; in clusters, however, such images have been seen (CITES)). We assumed for all our tests that the lensing mass
was radially symmetric ({\bf JR. Need to better-define this symmetry here.}. For our mock data, this is known to be true; it is
most often the case with real galaxies, unless there is an obvious observed
asymmetry. The central pixel was refined into a further nine pixels to capture
any steep rise in the profile. Two of the four mock galaxies have a steeply rising
inner profile. {\bf JR. What happens if we don't assume this symmetry? We ought to add an appendix showing this for one example case.}

\section{Results}\label{sec:results}
\figref{reconstruction} shows a typical reconstruction of a
lens. The far left plot shows the ensemble average arrival time surface with
image marked as circles and the inferred source position as a diamond. The
center plot shows the radial density profile. The error bars cover the full
range of models generated by \Glass {\bf JR. Why do this? Surely 1 or 2 sigma errors make more sense? I've deleted the ``full ensemble" results and kept the $1\sigma$ ones instead.}. The true density profile from the mock
data is also plotted for comparison. The vertical lines mark the radial
position of the images. The final plot on the right is of the enclosed mass. As
expected, the error bars are smallest in the region of the images where the most
information about the lens is present. The dip in the profile at the end of the
profile is due to the cut off in mass in the lensing map. This is of little
importance, though, as there is no lensing information there.

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-b.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-c.pdf}
\caption{
{\bf JR. Need to homogenise plot dimensions here. Larger fonts as in Figure 1 are also required.} 
A typical reconstructed lens. Here we present results for a single quad image lensed by the BC mock galaxy.
\textbf{Left:}
The arrival time surface. 
\textbf{Middle:}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The green vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{Right:}
The cumulative mass.}
\label{reconstruction}
\end{figure*}

The main results from modelling these different configuration are shown in black in
\figref{main results}. Each subplot corresponds to a different galaxy and
the vertical axis shows the range of `quality' of recovery, defined as: 
\begin{equation} \label{badness}
\chi^2 = \frac
       {\Big\langle \int \left|\Delta\Sigma(\vec{\theta})\right|^2 \,
        d^2 \vec{\theta} \Big\rangle}
       {\int \Sigma^2(\vec{\theta}) \; d^2 \vec{\theta}}
\end{equation}
where the angle brackets denote averages over the model ensemble.
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

\begin{figure*}
\includegraphics[width=0.49\textwidth]{AAchi2_profile.pdf}
\includegraphics[width=0.49\textwidth]{BBchi2_profile.pdf}\\
\includegraphics[width=0.49\textwidth]{ACchi2_profile.pdf}
\includegraphics[width=0.49\textwidth]{BCchi2_profile.pdf}
\caption{The main results showing the quality of model recovery. Each panel corresponds to 
the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
each panel are six groups of results for each of six lens morphologies. Each morphology
considered the presence of time delays and a central image. The black markers are for tests
that did not include the stellar mass as a lower bound constraint, while the red markers
indicate where the stellar mass has been given. Error bars show the $1\sigma$ equivalent interval sampled from the model ensemble.}
\label{main results}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.49\textwidth]{AAchi2-full.pdf}
\includegraphics[width=0.49\textwidth]{BBchi2-full.pdf}\\
\includegraphics[width=0.49\textwidth]{ACchi2-full.pdf}
\includegraphics[width=0.49\textwidth]{BCchi2-full.pdf}
\caption{{\bf JR. This should be also with $1\sigma$ errors. Also need to do this plot for Claudio's shape measure.} Pixel-wise $\chi$.}
\label{main results pixel-wise}
\end{figure*}

The abundance of strong lensing data increases from left to right within each plot. As
a result, there is a general trend for the reconstruction quality to increase
(and for $\chi$ to decrease). By adding more measurable information to each
configuration the quality can also be affected. When both time delays and a
central image are present the quality is highest. A double is known to provide
very little constraint on the mass distribution. This is particularly evident in
galaxies AC and BC where the mass profile is steepest and the reconstruction of
the double is poorest. However, the addition of an arc is sufficient to correct
this.

@@

\item Change variable $\chi$ to something else ($f$?) to avoid
  confusion with $\chi^2$.

\item Correct equation \eqref{badness} to describe what is actually
  calculated.

\item Show results for $1\sigma$ and $2\sigma$ rather than full
  \Glass\ ensemble.

@@

@@

\section{Derivation of pixelated density coefficients}
\label{Q derivation}
When the lens plane is pixelized we need a discrete form of the integral
%
\[\int \kappa(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta' \]
%
In particular we want
%
\[\sum_n \kappa_n Q_n(\vec\theta)\]
%
where $Q_n$ is the logarithm evaluated over the $n$th pixel at position $\vec\theta_n = (x_n, y_n)$. Let the pixel side length be $a$.
Instead of working with a position vector $\vec\theta$ we work in cartesian coordinates such that
%
$|\vec\theta| = r = \sqrt{x^2 + y^2}$. The integral now becomes
%
\[Q_n(x,y) = \frac12 \int_{y_-}^{y_+}\int_{x_-}^{x_+} \ln (x'^2+y'^2) dx' dy'\]
%
where $x_\pm = x + x_n \pm (a/2)$ and similarly for $y_\pm$.
Using the identity
%
\[\int \ln(x^2+y^2) dx = x \ln(x^2+y^2) - 2x + 2y\arctan(x/a) \]
%
we can express $Q_n$ as the sum of four parts
%
\[Q_n(x,y) = \frac12 \left[ \tilde Q_n(x_+,y_+)
        + \tilde Q_n(x_-,y_-)
        - \tilde Q_n(x_-,y_+)
        - \tilde Q_n(x_+,y_-) \right]\]
%
where
%
\[\tilde Q_n(x,y) = xy(\ln r^2 - 3) + x^2\arctan(y/x) + y^2\arctan(x/y)\]

>>>>

\documentclass[galley,usenatbib]{mn2e}
%\documentclass[twocolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
\usepackage{myaasmacros}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{ulem} % Only necessary for striking out TODO items see \sout

@@

\Glass\ is an evolution of the concepts employed by the free form modelling tool
\PixeLens\ but completely rewritten in Python and C. 
The most compute intensive
portion was written in C but Python was chosen because of its flexibility as a 
language and for its large scientific library support. The flexibility allows 
\Glass\ to have quite sophisticated behavior while at the same time simplfying the 
user experience and reducing the overall development time. One of the striking
features is that the input file to \Glass\ is itself a Python program.
Understanding Python is not necessary, however, to use \Glass\ but this allows
a user to build the analysis of a model directly into the input file. \Glass\
may also be used as an external library to other Python programs.  The software
is freely available for download or from the author.

The key scientific and technical improvements are:
%
\begin{enumerate}
  \setcounter{enumi}{0}
  \item A modular framework that allows new priors to be added and modified easily.
\end{enumerate}
%
Each prior is a simple function that adds linear constraints that operate on either
a single lens object or the entire ensemble of objects. \Glass\ comes with a number
of useful priors, the default ones will be described later, but a user can
write their own directly in the input file, or by modifying the source code.
%
\begin{enumerate}
  \setcounter{enumi}{1}
  \item The basis functions approximating a model can be changed. 
\end{enumerate}
%
\Glass\ currently describes the lens mass as a collection of pixels, but the code
has been designed to support alternative methods. In particular, there are future
plans to develop a module using Bessel functions. This will require a new set of 
priors that operate on these functions.
%
\begin{enumerate}
  \setcounter{enumi}{2}
  \item Non-linear constraints can be imposed in an automated post-processing step. 
\end{enumerate}
%
Once \Glass\ has generated an ensemble of models given the linear constraints, any number
of post processing functions can be applied. Not only can these functions be used to
derive new quantities from the mass models, they can also be used as a filter to 
accept or reject a model based on some non-linear constraint. The plotting functions
within \Glass\ will correctly display models that have been accepted or rejected.
%
\begin{enumerate}
  \setcounter{enumi}{3}
  \item The central region can be have a higher resolution to capture steep models. 
\end{enumerate}
%
With the default basis set of pixels, the mass distribution of the lens is
described by uniform grid. However, in the central region of a lensing galaxy
where the mass profile may rise steeply, the center pixel uses a higher
resolution. This allows the density to increase smoothly but still allow for
a large degree of freedom within the inner region without allowing the density
to be arbitrarily high. 
%
\begin{enumerate}
  \setcounter{enumi}{4}
  \item Stellar density can be used as an additional constraint.  
\end{enumerate}
%
The mass in inner regions of galaxies is often dominated by the stellar component
which one can estimate using standard mass-to-light models. This data can be added
to the potential as described later in \secref{stellar mass}. By using the stellar
mass one can place a lower bound on the mass and help constrain the inner most
mass profile.
%
\begin{enumerate}
  \setcounter{enumi}{5}
  \item Point or extended mass objects can be placed in the field.
\end{enumerate}
%
\PixeLens\ only allows for a shear term to be added to the potential (as shown
later in \eqnref{shear}) to account for mass external to model region. This
is useful to capture the gross effects of a distant neighbour. \Glass\ also
has a shear term but in addition allows for analytic potentials to
be included. This can be used to model substructure or multiple neighbors close
to the main lens. The substructure may have only a small effect if the lens is
a single galaxy, but if the lens is a group then a potential can be added for
each of the galaxies. A few standard functions are already included in \Glass\
including those for a point mass, a power law distribution, or an isothermal (a
particular case of the power law).
%
\begin{enumerate}
  \setcounter{enumi}{5}
  \item A new uniform sampling algorithm for high dimensional spaces.
\end{enumerate}
%
At the heart of \Glass\ lies a new algorithm for sampling the high dimensional
linear space that represents the modelling solution space. This algorithm was
described and tested in \cite{2012MNRAS.425.3077L}. This algorithm is 
multi-threaded allowing it to run efficiently on many-cored machines.

@@

\subsection{Analysis Tools}\label{sec:tools}
\Glass\ is not only a modeling tool but also an analysis engine. \Glass\
provides many functions for viewing and manipulating the computed models.
These functions can either be called from a program written by the user or 
by using the program \textsc{viewstate.py} included with \Glass. There is
also a tools, \textsc{lenspick.py} for creating a lens, either from an $N$-body
simulation file, or from an analytic form. To load the simluation data, \Glass\
uses \textsc{PynBody} and can thus load any file supported by that tool.

@@

Unfortunately, the lens equation and the arrival times alone are not enough to form a
closed volume in the solution space. We have not imposed any strong constraints
on the density even so much as to ensure that it is non-negative everywhere. We
must therefore provide additional linear constraints so that we only sample
physical models. The explicit implementation for these priors has been
explained in \cite{}, but can be summarized as
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope everywhere $\le 0$.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity is enforced.
\item The density is radially symmetric. (Optional)
\end{enumerate}

Prior (ii) is necessary to prevent rings from forming where the inner region is
less dense. This would be unusual for a galaxy or a cluster. Prior (vi)
enforces a radial symmetry that requires radially opposed pixels (i.e., on
opposite sides of the center) to be equal. This prior is particularly important
for modelling doubles which must be symmetric. If a lens is suspected to be
symmetric this can also significantly improve the modelling time for quads.

@@

\subsection{Removing models with extra images}\label{sec:glassextraimages} 
While linear constraints are applied in \Glass\ by the nature of the sampling
algorithm, non-linear constraints must be applied in post-processing. Models
that are inconsistent with such constraints must then be statistically
discarded via a likelihood analysis. An example of such a non-linear constraint
is the spurious presence of unobserved images. This `null-space' prior was
first proposed and explored by \citet{2006MNRAS.367.1209L} and found to be
extremely powerful. We find that our gradient prior in \Glass\ (see
\S\ref{sec:discrete}), performs much of the same function as
\citeauthor{2006MNRAS.367.1209L}'s null-space prior, but some models can still
rarely turn up spurious images. We reject these in a post-processing step,
where we sweep through the model ensemble applying the ray tracing algorithm
described in \ref{Raytracing}. Models are accepted or rejected according to the
criteria:

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{MockGalProfile-a.pdf} 
\includegraphics[width=0.33\textwidth]{MockGalProfile-b.pdf} 
\includegraphics[width=0.33\textwidth]{MockGalProfile-c.pdf}
\caption{{\bf JR. Cut the analytic profiles from this Figure. All fonts and labels should be larger. Left panel should start at 0.7kpc.}
\textbf{Left:} 
Spherically averaged density profiles of the four mock galaxies showing the stellar (dotted), dark matter (dashed),
and total (solid) densities. Notice that the stars in models Sdom/DMshallow and Sdom/DMcuspy contribute significantly to the central potential. 
\textbf{Middle:} 
The radially averaged two-dimensional projected density.
The critical density for lensing at $z_L=0.31$, $\kappa_\mathrm{crit}\sim 1.8\e{9}$\Msun/kpc$^2$, is marked by the horizontal line. 
\textbf{Right:}
The enclosed projected mass.
}
\label{mock galaxies}
\end{figure*}

@@

For each of the four galaxies, we used the raytracing feature of \Glass\
described in \secref{Raytracing} to construct 6 basic lensing morphologies:

\begin{enumerate}
\item one double and one extended double;
\item one quad and one extended quad;
\item two 2-source quads with varying redshift contrast.
\end{enumerate}
The `extended' configurations use multiple point sources at the same redshift
to simulate an extended source that will produces an arc-like image.
\figref{arrival surfaces} shows the configuration for the extended quad, along
with the other cases.

@@

Each of these configurations were modelled with and without time delays and
with and without a central image, for a total of 24 test cases. (The central
image is typically highly demagnified. For galaxy lenses it is very difficult
to find since it lies along the sight line to the bright lensing galaxy; in
clusters, however, such images have been seen (CITES)). We assumed for all our
tests that the lensing mass was radially symmetric (Prior vi):
For our mock data, this is known to be
true; it is most often the case with real galaxies, unless there is an obvious
observed asymmetry. The central pixel was refined into a further nine pixels to
capture any steep rise in the profile.  Two of the four mock galaxies have a
steeply rising inner profile. {\bf JR.  What happens if we don't assume this
symmetry? We ought to add an appendix showing this for one example case.}

\section{Results}\label{sec:results}
\figref{reconstruction} shows a typical reconstruction of a
lens. The far left plot shows the ensemble average arrival time surface with
image marked as circles and the inferred source position as a diamond. The
center plot shows the radial density profile. The error bars cover the full
range of models generated by \Glass {\bf JR. Why do this? Surely 1 or 2 sigma
errors make more sense? I've deleted the ``full ensemble'' results and kept the
$1\sigma$ ones instead.}. The true density profile from the mock data is also
plotted for comparison. The vertical lines mark the radial position of the
images. The final plot on the right is of the enclosed mass. As expected, the
error bars are smallest in the region of the images where the most information
about the lens is present. The dip in the profile at the end of the profile is
due to the cut off in mass in the lensing map. This is of little importance,
though, as there is no lensing information there.

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-b.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-c.pdf}
\caption{
  \sout{{\bf JR. Need to homogenise plot dimensions here. Larger fonts as in Figure 1 are also required.} }
A typical reconstructed lens. Here we present results for a single quad image lensed by the Sdom/DMcuspy mock galaxy.
\textbf{Left:}
The arrival time surface. 
\textbf{Middle:}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The green vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{Right:}
The cumulative mass. The error bars on both plots are $1\sigma$.}
\label{reconstruction}
\end{figure*}

The main results from modelling these different configurations are shown in black in
\figref{main results} and \figref{main results pixel-wise}. Each subplot corresponds to a different galaxy and
the vertical axis shows the range of `quality' of recovery. In \figref{main results}, this quality is
defined over radial bins of mass as
%
\begin{equation} \label{badness}
  f_r = \frac {\int \left|\Delta M(r)\right|\; dr } {\int M(r)\; dr}
\end{equation}
%
while in \figref{main results pixel-wise} the quality is defined over all the pixels
%
\begin{equation} \label{badness}
f_\theta = \frac
       {\int \left|\Delta M(\vec\theta)\right| \; d \vec{\theta} }
       {\int M(\vec\theta) \; d \vec\theta}
\end{equation}
In both cases, the delta difference is between a single recovered model and the known mock galaxy.
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

\begin{figure*}
\includegraphics[width=0.49\textwidth]{AAferror_profile-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BBferror_profile-1sig.pdf}\\
\includegraphics[width=0.49\textwidth]{ACferror_profile-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BCferror_profile-1sig.pdf}
\caption{The main results showing the quality of model recovery. Each panel corresponds to 
the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
each panel are six groups of results for each of six lens morphologies. Each morphology
considered the presence of time delays (T/t) and a central image (M/m). The black markers are for tests
that did not include the stellar mass as a lower bound constraint, while the red markers
indicate where the stellar mass has been given. Error bars show the $1\sigma$ equivalent interval sampled from the model ensemble.}
\label{main results}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.49\textwidth]{AAferror-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BBferror-1sig.pdf}\\
\includegraphics[width=0.49\textwidth]{ACferror-1sig.pdf}
\includegraphics[width=0.49\textwidth]{BCferror-1sig.pdf}
\caption{ {\bf JR. \sout{ This should be also with $1\sigma$ errors.} Also need to do this plot for Claudio's shape measure.} \sout{Pixel-wise $\chi$.}
The fractional error for the pixel-wise recovery of all models. The colors and labels are the same as in \figref{main results}. Error bars show the $1\sigma$ equivalent interval sampled from the model ensemble.}
\label{main results pixel-wise}
\end{figure*}

The abundance of strong lensing data increases from left to right within each plot. As
a result, there is a general trend for the reconstruction quality to increase
(and for $f$ to decrease). By adding more measurable information to each
configuration the quality can also be affected. When both time delays and a
central image are present the quality is highest. A double is known to provide
very little constraint on the mass distribution. This is particularly evident in
galaxies AC and BC where the mass profile is steepest and the reconstruction of
the double is poorest. However, the addition of an arc is sufficient to correct
this.

@@

  \item \sout{Change variable $\chi$ to something else ($f$?) to avoid confusion with $\chi^2$.}

  \item \sout{Correct equation \eqref{badness} to describe what is actually calculated.}

  \item \sout{Show results for $1\sigma$ and $2\sigma$ rather than full \Glass\ ensemble.}

@@

\section{Implementation Details}

Since we want to model the density distribution with a computer it
is convenient to choose units that make the relevant quantities of order
unity.  We therefore measure lengths in light years, time in years, positions
in arcseconds, and choose $c=1$ and $4\pi G = N^2$, where $N^2 \equiv 206,265$
arcsec/rad. The mass unit is then $11.988\ \Msun$. It will also be useful to
define a proxy to the Hubble constant $\zeta \equiv N^2 H_0$. We now 
express the equations from \secref{sec:theory} in terms of these new units
and introduce some other useful quantities.

The lens equation in its complete form becomes:
%
\begin{eqnarray}
N^2ct(\vec\theta) & = & (1+z_L)\frac{D_{L}D_{S}}{D_{LS}}\frac12 |\vec\theta - \vec\beta|^2 \nonumber \\
& & - (1+z_L)\frac{4GD_{L}^2}{c^2}\int \Sigma(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta'
\label{eqn:full_arrival_time}
\end{eqnarray}
%
where the factor of $D_L^2$ in the second term comes from the fact that $\Sigma$
has units of \Msun/lyr$^2$. We can clean this up by writing down a dimensionless time
delay:
%
\begin{equation}
\tau = \left[ (1+z_L) d_L\right]^{-1}\zeta t
\label{tau}
\end{equation}
%
in terms of our previous definitions. If we
further define a dimensionless density:
%
\begin{equation}
\kappa_\infty = \frac{4\pi G}{c^2}\frac{c}{H_0}d_L\Sigma
              = \frac{d_L}{\zeta}\Sigma
\end{equation}
%
and a lensing potential:
%
\begin{equation}
\psi(\vec\theta) = \frac1\pi \int \kappa_\infty(\vec\theta') \ln|\vec\theta - \vec\theta'| d^2\vec\theta'\
\label{lensing potential}
\end{equation}
%
we can express \eqnref{eqn:full_arrival_time} very compactly as:
%
\begin{equation}
\tau(\vec\theta) = \frac12 \xi |\vec\theta-\vec\beta|^2 - \psi(\vec\theta)
\label{arrival time}
\end{equation}
We explicitly write $\kappa_\infty$ to remind ourselves
that there is no source distance factor involved. This is useful when we
consider multiple sources.

@@

\section{Derivation of pixelated density coefficients}
\label{Q derivation}
When the lens plane is pixelized we need a discrete form of the integral
%
\[\int \kappa(\vec\theta') \ln |\vec\theta-\vec\theta'| d^2\vec\theta' \]
%
In particular we want
%
\[\sum_n \kappa_n Q_n(\vec\theta)\]
%
where $Q_n$ is the logarithm evaluated over the $n$th pixel at position $\vec\theta_n = (x_n, y_n)$. Let the pixel side length be $a$.
Instead of working with a position vector $\vec\theta$ we work in cartesian coordinates where 
%
$|\vec\theta| = r = \sqrt{x^2 + y^2}$. The integral now becomes
%
\[Q_n(x,y) = \frac12 \int_{y_-}^{y_+}\int_{x_-}^{x_+} \ln (x'^2+y'^2) dx' dy'\]
%
where $x_\pm = x + x_n \pm (a/2)$ and similarly for $y_\pm$.
Using the identity
%
\[\int \ln(x^2+y^2) dx = x \ln(x^2+y^2) - 2x + 2y\arctan(x/a) \]
%
we can express $Q_n$ as the sum of four parts
%
\[Q_n(x,y) = \frac12 \left[ \tilde Q_n(x_+,y_+)
        + \tilde Q_n(x_-,y_-)
        - \tilde Q_n(x_-,y_+)
        - \tilde Q_n(x_+,y_-) \right]\]
%
where
%
\[\tilde Q_n(x,y) = xy(\ln r^2 - 3) + x^2\arctan(y/x) + y^2\arctan(x/y)\]
